Hydras \& Co.

### 2022-05-24 doc/hydra-chapter.tex
small corrections

Let us define a binary relation associated with every round of the battle.
In the following definition \texttt{i} is associated with the round number (or date, if we consider a discrete time), and \texttt{a}, \texttt{b}, \texttt{c} respectively associated with the number of occurrences of \texttt{h2}, \texttt{h1} and heads connected to the hydra's foot. For convenience, we do not use the type \texttt{state} of the preceeding section, but consider the round numbers and the number of hydras \texttt{h2}, \texttt{h1} and heads as separate arguments of the relation (which is no more ---formally--- ``binary'').

>>>>

Let us define a binary relation associated with every round of the battle.
In the following definition \texttt{i} is associated with the round number (or date, if we consider a discrete time), and \texttt{a}, \texttt{b}, \texttt{c} respectively associated with the number of occurrences of \texttt{h2}, \texttt{h1} and heads connected to the hydra's foot. For convenience, we do not use the type \texttt{state} of the preceding section, but consider the round numbers and the number of hydras \texttt{h2}, \texttt{h1} and heads as separate arguments of the relation (which is no more ---formally--- ``binary'').
